Demystifying the Combination of Dynamic Slicing and \\ Spectrum-based Fault Localization

### 2019-02-26 paper/ijcai/paper.tex
pass on conclusion

Several approaches have been proposed in the literature to improve debugging
costs through automated software fault diagnosis to reduce time-to-market,
while maintaining high quality standards. In this domain, Dynamic Slicing (\ds)
and Spectrum-based Fault Localization (\sfl) are very popular fault diagnosis
techniques and normally seen as complementary. This paper reports the outcome of
a study using real-world applications with the goal of demystifying the impact
of combining \ds~with \sfl. The results of our empirical study show that, in
practice, \ds~rarely misses faulty statements $9\%$ ($23$ misses in $260$ cases) and that
the \ds-\sfl~combination, coined as \combpar{k},
improves the diagnostic accuracy up to $73.7\%$ ($13.4\%$ on average).
Hence, we found that, despite tacit opinions of the research community about
the usefulness of \ds~in automated debugging, we found the combination practical
and effective, and encourage new \sfl~techniques to be evaluated against that
optimization.
Future work is as follows: improve our oracle heuristics to handle more exceptions;
conduct experiments in more \dfj{} faults or other datasets; find techniques to
handle the cases which harm the cost of diagnosis, such as, faults of omission,
test design problems and the cases which the buggy-class is not in the top-$k$ of
highest-rank faulty classes.

>>>>

Several approaches have been proposed in the literature to reduce debugging
costs through automated software fault diagnosis with the goal of
improving productivity in software developement. In this domain, Dynamic Slicing (\ds)
and Spectrum-based Fault Localization (\sfl) are very popular fault diagnosis
techniques and normally seen as complementary. This paper reports the outcome of
a study using real-world applications with the goal of demystifying the impact
of combining \ds~with \sfl. The results of our empirical study show that, in
practice, \ds~rarely misses faulty statements $9\%$ ($23$ misses in $260$ cases) and that
the \ds-\sfl~combination, coined as \combpar{k},
improves the diagnostic accuracy up to $73.7\%$ ($13.4\%$ on average).

Despite tacit opinions of the research community about the usefulness
of \ds~in automated debugging, we found te \ds{}-\sfl{} combination
practical (as per the relatively low number of misses) and effective
(as per the improvements of $\Delta(C)$ on the relevant cases), and
encourage new \sfl~techniques to be evaluated against that
optimization.  Future work includes 1)~improving our oracle heuristics
to handle more exceptions, 2)~conducting experiments in more \dfj{}
faults and other datasets, and 3)~handling cases of faults of
omission.

The dataset and tools (Lithium slicer and \comb{}) will be made
available once double-blind requirements are lifted.

%% the
%% cases which harm the cost of diagnosis, such as, faults of omission,
%% test design problems and the cases which the buggy-class is not in the
%% top-$k$ of highest-rank faulty classes.
